### 2016-10-04 paper/numerical_experiments_v2.tex
made edits to numerical results section, awaiting comments on intro from karen

The domain divisions for the five adaptive iterations are shown in \cref{fig:divvy3D_diffmesh}. Similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to be refined around. We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_1$ ($5.2\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff.png} 
}
\subfloat[MF$_2$ ($11.4\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff.png} 
}
\subfloat[MF$_3$ ($16.3\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff.png} 
} \\
\subfloat[MF$_4$ ($22.0\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff.png} 
}
\subfloat[MF$_5$ ($27.7\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff.png} 
}
\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
\label{fig:divvy3D_diffmesh}
\end{figure} 
%
In this case, although the mixed-fidelity models have fewer degrees of freedom than the high-fidelity model, it is faster to solve the high-fidelity inverse problem than to adaptively seek a mixed-fidelity model with a small QoI error, starting from the low-fidelity model. This can be attributed to multiple factors: the high-fidelity problem is mildly nonlinear and has a close initial guess that is a solution to a linear system (when $k_r=0$), and the supplementary adjoint is solved on the high-fidelity mesh. Generally, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm as the nonlinearity of the high-fidelity model increases.

To illustrate the first offline-online application described in \cref{sec:onoff}, we generate ten sets of noisy observations to represent the actual data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to, on average, $5\%$ of the observed values). We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model. The low-fidelity inverse problem is first solved and used as an initial guess for the higher-fidelity problems; we note that although there is a linear model that is more similar to the high-fidelity model than the low-fidelity model (i.e., convection-diffusion with anisotropic diffusivity and $k_r=0$ on the high-fidelity mesh) and thus would serve as a better initial guess, its existence is specific to our particular choice of models. The auxiliary and supplementary adjoint variables simply have a zero initial guess.

@@

In testing this online-offline setting with a larger range of datasets, we would like to note some additional observations. Suppose one has two datasets $d_1$ and $d_2$, the latter of which one wishes to perform inference. For a fixed proportion of domain refinement, a mixed-fidelity model that was adaptively generated $d_2$ gives a smaller QoI error than a mixed-fidelity model that was generated based on $d_1$. The performance gap tends to widen as the two datasets become more different. Suppose one generated $d_1$ using the high-fidelity model $d_2$ using a model which differed from the high-fidelity model in its domain, boundary conditions, and reaction coefficient; then a mixed-fidelity model adaptively formed based on $d_1$ might not give a low QoI error when used to infer from $d_2$. However, when the adaptivity algorithm is directly applied to this $d_2$, it is still able to find a mixed-fidelity model with a low QoI error. This behavior suggest that, if resources allow, it is best to perform the adaptivity online with the true observations. If one is confident that one's high-fidelity model is a good approximation of reality, then the online-offline approach can potentially give a faster yet accurate QoI estimate.

>>>>

The domain divisions for the five adaptive iterations are shown in \cref{fig:divvy3D_diffmesh}. Similarly to the behavior seen in \cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to be refined around. We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, possibly reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_1$ ($5.2\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff.png} 
}
\subfloat[MF$_2$ ($11.4\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff.png} 
}
\subfloat[MF$_3$ ($16.3\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff.png} 
} \\
\subfloat[MF$_4$ ($22.0\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff.png} 
}
\subfloat[MF$_5$ ($27.7\%$ HF)]{
\includegraphics[width=0.31\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff.png} 
}
\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
\label{fig:divvy3D_diffmesh}
\end{figure} 
%
In this case, although the mixed-fidelity models have fewer degrees of freedom than the high-fidelity model, it is faster to solve the high-fidelity inverse problem than to adaptively seek a mixed-fidelity model with a small QoI error, starting from the low-fidelity model. This can be attributed to multiple factors: the high-fidelity problem is mildly nonlinear and has a close initial guess that is a solution to a linear system (when $k_r=0$), and the supplementary adjoint is solved on the high-fidelity mesh. Generally, as the nonlinearity of the high-fidelity model increases, one would expect solving the high-fidelity inverse problem to require more time relative to using the adaptive algorithm.

\Cref{alg:refSeries} can be naturally extended to an offline-online setting, where \Cref{alg:refSeries} is first run offline to adaptively create a mixed-fidelity model with an appropriate error tolerance given some expected observations $d^*$. When new data is received, one can then solve the inverse problem with the chosen mixed-fidelity model and the new data, and, if desired, compute an error estimate for the QoI. The mixed-fidelity inverse problems can be expected to require less time to solve than the high-fidelity inverse problems.

To illustrate this offline-online application, we generate ten sets of noisy observations to represent the actual data gained during the online phase; the noisy observations are generated by taking the observations used in the adaptive algorithm and adding Gaussian white noise with standard deviation of $\sigma=0.02$ (equivalent to, on average, $5\%$ of the observed values). We then solve the inverse problem using each of the mixed-fidelity models depicted in \cref{tab:ref3D_diffmesh,fig:divvy3D_diffmesh} as well as the high-fidelity model. The low-fidelity inverse problem is first solved and used as an initial guess for the higher-fidelity problems; we note that although there is a linear model that is more similar to the high-fidelity model than the low-fidelity model (i.e., convection-diffusion with anisotropic diffusivity and $k_r=0$ on the high-fidelity mesh) and thus would serve as a better initial guess, its existence is specific to our particular choice of models. The auxiliary and supplementary adjoint variables simply have a zero initial guess.

@@

In testing this online-offline setting with a larger range of datasets, we would like to note some additional observations. Suppose one has two datasets $d_1$ and $d_2$, the latter of which one wishes to perform inference on. For a fixed proportion of domain refinement, a mixed-fidelity model that was adaptively generated $d_2$ gives a smaller QoI error than a mixed-fidelity model that was generated based on $d_1$. The performance gap tends to widen as the two datasets become more different. Suppose one generated $d_1$ using the high-fidelity model $d_2$ using a model which differed from the high-fidelity model in its domain, boundary conditions, and reaction coefficient; then a mixed-fidelity model adaptively formed based on $d_1$ might not give a low QoI error when used to infer from $d_2$. However, when the adaptivity algorithm is directly applied to this $d_2$, it is still able to find a mixed-fidelity model with a low QoI error. This behavior suggest that, if resources allow, it is best to perform the adaptivity online with the true observations. If one is confident that one's high-fidelity model is a good approximation of reality, then the online-offline approach can potentially give a faster yet accurate QoI estimate.
